---
title: "analysis preliminar trastornos mentales postpandemia"
author: "Marc Bañuls Tornero"
date: "10/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(oddsratio)
```


# Regression analyses CONTENT variables for multiactor survey


Get REDCap CONTENT data:

```{r}
content_data <- read.csv("CONTENTGCAT_DATA_2021-11-10_1659.csv")
```

Filter by complete questionnaires:
```{r}
content_data <- content_data[content_data$cuestionario_content_complete == 2,]
```

#variables

"area salud mental"
G16 (help_mental_health) yes, no
G17 (regional_resources) yes, no, servicio privado
G18 (affirmations) escala 0 to 10

"Asistencia sanitaria de patologia no covid"
H01 (private_health) yes, no
i21 (medical aid confinement) yes, no

"Violencia contra la mujer y violencia doméstica"
G20 (violence) 0nunca 1aveces 2muchasveces
G21a (violence_where__1,2,3,4) yes no para cada uno
G21b (help_violence) yes no
G21c (help_violence_quality) escala 0 10
G22 (physical_violence) 0nunca 1aveces 2muchasveces
G22a (violence_lesions_medical_attention) yes no
g22b (lesions_where__1,2,3) yes no para cada uno
G22c (help_physical_violence) yes no
G22d (help_physical_violence_quality) escala 0 a 10

```{r}
names_violence_factor <- c("violence", "violence_where___1",  "violence_where___2",  "violence_where___3",  "violence_where___4", "help_violence", "physical_violence", "violence_lesions_medical_attention", "lesions_where___1", "lesions_where___2", "lesions_where___3", "help_physical_violence" )
```

```{r}
content_data[, names_violence_factor] <- lapply(content_data[, names_violence_factor], factor)
```



"Conciliación laboral y cuidados (con perspectiva de género)
por resolver

"desigualdades sociles, pérdida de empleo e ingresos"
I13 (work_change_informal__1,5) 1 to 5 y 88 (cada uno una cosa)
I14 (work_change_formal__1,5) 1 to 5 (cada uno una cosa)
J01 (study_level) 1 to 7 88otros y 77nose
J02 (income_family_unit) 1 to 6  77noresponde
J02b (change_income_familiar_unit) 1sube 2 baja 0 mantiene
J02c (increase_income_specific) 1 si 77noresponde
J02c1 (increase_income_specific2) unidades
J02d (decrease_income_specific) 1 si 77noresponde
J02d1 (decrease_income_specific2)unidades
J02f (aids_pandemic) 0no 1 to 6 cosas 88otros
J03 condición de migrantes..?

```{r}
names_laboral_and_care <- c("work_change_informal", "work_change_formal___1", "work_change_formal___2", "work_change_formal___3", "work_change_formal___4", "work_change_formal___5", "study_level", "income_family_unit", "change_income_familiar_unit", "increase_income_specific", "decrease_income_specific", "aids_pandemic")
```

```{r}
content_data[, names_laboral_and_care] <- lapply(content_data[, names_laboral_and_care], factor)
```

```{r}
str(content_data$change_income_familiar_unit)
```



"extra"
A01 (age) unidades
A02 (gender) 1 hombre 2 mujer 88 otros

```{r}
content_data$gender <- as.factor(content_data$gender)
```

```{r}
table(content_data$gender)
```


## ment_postpand regresion

ment_postpand (chronic_illnes_type_14 == 1):

### salud mental


Change variables to factors (the ones needed):
```{r}
content_data$help_mental_health <- as.factor(content_data$help_mental_health)
content_data$regional_resources <- as.factor(content_data$regional_resources)
```




change to categorical data ment_postpand variable:
```{r}
content_data$chronic_illnes_type_14 <-as.factor(content_data$chronic_illnes_type_14)
```

```{r}
ment_postpand_help_mental_health <- glm(content_data$chronic_illnes_type_14 ~ content_data$help_mental_health, family =binomial)
```

```{r}
summary(ment_postpand_help_mental_health)
```

```{r}
or_glm(content_data, ment_postpand_help_mental_health)
```

The response (having ment_postpand) is 14 times more likely to occur when the participant has the need to look for mental health professionals

```{r}
ment_postpand_regional_resources <- glm(chronic_illnes_type_14 ~regional_resources, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_regional_resources)
```

```{r}
or_glm(content_data, ment_postpand_regional_resources)
```
Is 7 times more likely that the participant has ment_postpand if the person has accessed to autonomic/statal resources during the pandemic, and 2 times more likely if it has used a private service.

```{r}
ment_postpand_affirmations <- glm(chronic_illnes_type_14 ~ affirmations, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_affirmations)
```

```{r}
or_glm(content_data, ment_postpand_affirmations, incr = list(affirmations = 1))
```

The quality of the mental health resources does not seem to change the likelihood of having ment_postpand


These variables cannot be in the same logit regression because they interact with each other if the person does not see the need of mental health help (help_mental_health) the variables for if it attended mental health resources and the quality of it would be null, thus the coefficient for this variable would be null (as when setting the other variables to its reference it nullifies the participants who wanted mental health care)


### Asistencia sanitaria de patologia no covid

```{r}
content_data$private_health <- as.factor(content_data$private_health)
content_data$medical_aid_confinement <- as.factor(content_data$medical_aid_confinement)
```


```{r}
ment_postpand_private_health <- glm(content_data$chronic_illnes_type_14 ~ content_data$private_health + content_data$medical_aid_confinement, family =binomial)
```

```{r}
summary(ment_postpand_private_health)
```

```{r}
or_glm(content_data, ment_postpand_private_health)
```

Here we see that people is more likely to have ment_postpand if they got medical aid during the confinement but there is no significant difference about accessing or not private health. 

###  Violence

"violence", "violence_where___1",  "violence_where___2",  "violence_where___3",  "violence_where___4", "help_violence", "physical_violence", "violence_lesions_medical_attention", "lesions_where___1", "lesions_where___2", "lesions_where___3", "help_physical_violence" )



```{r}
ment_postpand_violence <- glm(chronic_illnes_type_14 ~ violence, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_violence)
```

```{r}
or_glm(content_data, ment_postpand_violence)
```
Both values are significant. If there were sometimes or many times violence during the pandemic it increased 4 to 8 times the likelihood of having ment_postpand.


```{r}
ment_postpand_violence_where <- glm(chronic_illnes_type_14 ~ violence_where___1 + violence_where___2 + violence_where___3 + violence_where___4, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_violence_where)
```

```{r}
or_glm(content_data, ment_postpand_violence_where)
```

It is more likely that the person has ment_postpand if the violence is in the home (6 times more). the other values are not significant enough, but could be that having violence in virtual context could increase 4.5 times the likelihood of having ment_postpand.


```{r}
ment_postpand_help_violence <- glm(chronic_illnes_type_14 ~ help_violence, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_help_violence)
```

```{r}
or_glm(content_data, ment_postpand_help_violence)
```


No significant


```{r}
ment_postpand_physical_violence <- glm(chronic_illnes_type_14 ~ physical_violence, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_physical_violence)
```

```{r}
or_glm(content_data, ment_postpand_physical_violence)
```

physical_violence no significant

violence_lesions_medical_attention
```{r}
table(content_data$violence_lesions_medical_attention)
```

```{r}
#ment_postpand_violence_lesions_medical_attention <- glm(chronic_illnes_type_14 ~ violence_lesions_medical_attention, data = content_data, family = binomial)
```

```{r}
#summary(ment_postpand_violence_lesions_medical_attention)
```

```{r}
#or_glm(content_data, ment_postpand_violence_lesions_medical_attention)
```

non significant


lesions_where___1

```{r}
ment_postpand_lesions_where <- glm(chronic_illnes_type_14 ~ lesions_where___1 + lesions_where___2 + lesions_where___3, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_lesions_where)
```

```{r}
or_glm(content_data, ment_postpand_lesions_where)
```


non significant.


help_physical_violence

```{r}
ment_postpand_help_physical_violence <- glm(chronic_illnes_type_14 ~ help_physical_violence, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_help_physical_violence)
```

```{r}
#or_glm(content_data, ment_postpand_help_physical_violence)
```




Non significant either

# Work changes

"work_change_informal", "work_change_formal___1", "work_change_formal___2", "work_change_formal___3", "work_change_formal___4", "work_change_formal___5", "study_level", "income_family_unit", "change_income_familiar_unit", "increase_income_specific", "decrease_income_specific", "aids_pandemic"

help_physical_violence

```{r}
ment_postpand_work_change_informal <- glm(chronic_illnes_type_14 ~ work_change_informal, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_work_change_informal)
```

```{r}
or_glm(content_data, ment_postpand_work_change_informal)
```

There are no significant changes in the odds ratio.

work_change_formal

```{r}
#ment_postpand_work_change_formal <- glm(chronic_illnes_type_14 ~ work_change_formal___1 + work_change_formal___2 + work_change_formal___3 + work_change_formal___4 + work_change_formal___5, data = content_data, family = binomial)
```

```{r}
#summary(ment_postpand_work_change_formal)
```

```{r}
#or_glm(content_data, ment_postpand_work_change_formal)
```

no significant changes


study_level
```{r}
ment_postpand_study_level <- glm(chronic_illnes_type_14 ~ study_level, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_study_level)
```
```{r}
table(content_data$study_level)
```

```{r}
or_glm(content_data, ment_postpand_study_level)
```

no significant differences either


income_family_unit

```{r}
ment_postpand_income_family_unit <- glm(chronic_illnes_type_14 ~ income_family_unit, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_income_family_unit)
```

```{r}
or_glm(content_data, ment_postpand_income_family_unit)
```

Although it is not significant at the 95% confidence, it looks like that when the income family unit is higher the lower likelihood is to be depressed.

increase_income_specific

```{r}
ment_postpand_increase_income_specific <- glm(chronic_illnes_type_14 ~ increase_income_specific, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_increase_income_specific)
```

```{r}
or_glm(content_data, ment_postpand_increase_income_specific)
```

No significant differences

decrease_income_specific


```{r}
ment_postpand_decrease_income_specific <- glm(chronic_illnes_type_14 ~ decrease_income_specific, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_decrease_income_specific)
```

```{r}
or_glm(content_data, ment_postpand_decrease_income_specific)
```


No significant changes either


aids_pandemic

```{r}
ment_postpand_aids_pandemic <- glm(chronic_illnes_type_14 ~ aids_pandemic, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_aids_pandemic)
```

```{r}
or_glm(content_data, ment_postpand_aids_pandemic)
```

no significant changes

### extra

age
```{r}
ment_postpand_age <- glm(chronic_illnes_type_14 ~ age, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_age)
```

```{r}
or_glm(content_data, ment_postpand_age, incr = list(age = 1))
```

no significances with age



gender
```{r}
ment_postpand_gender <- glm(chronic_illnes_type_14 ~ gender, data = content_data, family = binomial)
```

```{r}
summary(ment_postpand_gender)
```

```{r}
or_glm(content_data, ment_postpand_gender)
```

There are significant results with this variable. I 2 times more likely to have ment_postpand if the participant is a woman than a man. Regarding other genders there is no significance.


















